---
title: "stream physical habitat"
author: "Emma Brentjens"
date: "2025-05-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

##setting working directory and loading data
current_wd <- getwd()
setwd(current_wd)
stream_data <- read.csv("20250225_wqp_wqx_bss_wq_npsncrn.csv")
colnames(stream_data)
head(stream_data)
#View(stream_data)

##filtering for columns of interest
filter_1 <- stream_data[, c("ActivityStartDate", "MonitoringLocationIdentifier",
                       "MonitoringLocationName", "CharacteristicName", 
                       "ResultMeasureValue", "ResultMeasure.MeasureUnitCode")]
nrow(filter_1)

##converting date to a date object
filter_1$ActivityStartDate <- as.Date(filter_1$ActivityStartDate, format = "%Y-%m-%d")
class(filter_1$ActivityStartDate)

##creating year column
#install.packages("lubridate")
library(lubridate)
filter_1$year <- year(filter_1$ActivityStartDate)
filter_1$month <- month(filter_1$ActivityStartDate)

#install.packages("dplyr")
library(dplyr)
#install.packages("tidyr")
library(tidyr)

library(ggplot2)

#install.packages("scales")
library(scales)

#install.packages("lemon")
library(lemon)

#install.packages("ggh4x")
library(ggh4x)

library(ggnewscale)

#install.paclages("xfun")
library(xfun)

library(ggtext)

```

Filtering for SPH
```{r}
sph <- filter_1 %>%
  filter(CharacteristicName %in% c("embeddedness - percentage of rocks (gravel, cobble, boulders) covered by sediment (sand, silt)",
                               "habitat quality - riffle", "habitat quality - pool, glide, eddy", "habitat quality - water velocity and depth",
                               "habitat quality - epifaunal substrate", "habitat quality - instream habitat")) %>%
  separate(MonitoringLocationIdentifier, c("Network", "Park", "Site")) %>%
  select(ActivityStartDate, Park, Site, MonitoringLocationName, CharacteristicName, ResultMeasureValue, year, month)

sph$ResultMeasureValue <- as.numeric(sph$ResultMeasureValue)
class(sph$ResultMeasureValue)

nrow(sph)
unique(sph$CharacteristicName)
#View(sph)

```

Exceedances function
```{r}
exceed <- function(df) {

df %>%
    mutate(is_embed=case_when(characteristic=="embed"~ T,
                            characteristic!="embed"~ F)) %>%
  mutate(over_55=case_when(value>=55 ~ "over_55", value<55 ~ "N")) %>%
  mutate(under_5=case_when(value<=5 ~ "under_5", value>5 ~ "N")) %>%
  mutate(paste_embed = paste0(characteristic, over_55)) %>%
  mutate(paste_quality = paste0(characteristic, under_5)) %>%
  mutate(embed_exceed=case_when(paste_embed=="embedover_55"~ T,
                                paste_embed!="embedover_55"~ F)) %>% 
  mutate(quality_exceed=case_when(characteristic=="embed"~ F,
                                  paste_quality=="epifaunN" | paste_quality=="velocity_depthN" |
                                    paste_quality=="riffleN" | paste_quality=="instreamN" |
                                    paste_quality=="poolN" ~ F,
                                  paste_quality=="epifaununder_5" | paste_quality=="velocity_depthunder_5" |
                                    paste_quality=="riffleunder_5" | paste_quality=="instreamunder_5" |
                                  paste_quality=="poolunder_5" ~ T)) %>%
  mutate(exceed=case_when(characteristic=="embed" & embed_exceed==T ~ T,
                          characteristic!="embed" & quality_exceed==T ~ T,
                          embed_exceed==F & quality_exceed==F ~ F)) %>%
  select(!c(over_55, under_5, paste_embed, paste_quality, embed_exceed, quality_exceed))

}

```


CATO habitat graph
```{r}
cato <- sph %>%
  subset(Park=="CATO" & (year==2010 | year==2022) & month>3) %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="embeddedness - percentage of rocks (gravel, cobble, boulders) covered by sediment (sand, silt)" ~ "embed",
                   CharacteristicName=="habitat quality - riffle" ~ "riffle",
                   CharacteristicName=="habitat quality - pool, glide, eddy" ~ "pool",
                   CharacteristicName=="habitat quality - water velocity and depth" ~ "velocity_depth",
                   CharacteristicName=="habitat quality - epifaunal substrate" ~ "epifaun",
                   CharacteristicName=="habitat quality - instream habitat" ~ "instream")) 

colnames(cato)[5:6]=c("characteristic", "value")

cato <- exceed(cato)


cato_habitat <- cato %>%
  filter(!characteristic=="embed") %>%
  mutate(x.axis=case_when(characteristic=="epifaun" ~ 1,
                          characteristic=="instream" ~ 2,
                          characteristic=="pool" ~ 3,
                          characteristic=="riffle" ~ 4,
                          characteristic=="velocity_depth" ~ 5))

cato_habitat_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.3, xmax=5.7, ymin=15, ymax=20, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=10, ymax=15, fill="#8ba7d6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=5, ymax=10, fill="#cf93b6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=0, ymax=5, fill="#f27c7e", alpha=0.5) +
  ##threshold lines
  geom_hline(yintercept=5, linetype="dashed", color="gray55") +
  geom_hline(yintercept=10, linetype="dashed", color="gray55") +
  geom_hline(yintercept=15, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=cato_habitat, aes(x=as.factor(x.axis), y=value, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white")) +
  ##facet grid
  facet_wrap2(.~MonitoringLocationName, axes="all", remove_labels="y",
              strip=strip_split("bottom")) +
  geom_text(data=cato_habitat[cato_habitat$value==0,], aes(x=as.factor(x.axis), y=value), label="•",
            position=position_nudge(x=-0.2), vjust=-0.1, size=6) +
  scale_x_discrete(labels=c("Epifaunal", "Instream", "Pool", "Riffle", "Velocity"),
                   guide=guide_axis(angle = 40)) +
  ##labels
  xlab("Stream") +
  ylab("Score") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 20), xlim=c(0.3, 5.7), clip="off", expand=F) +
  ##habitat quality color scale
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  ##theme
  theme_bw(base_size=15) +
  theme(strip.placement="outside",
        axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=10),
        axis.title.y = element_text(size=20, vjust=7),
        axis.title.x=element_text(size=20, vjust=-0.75), 
        strip.text = element_text(size=15),
        plot.margin=margin(t = 0.5, r = 1, b = 0.5, l = 1.5, unit = "cm"),
        panel.spacing=unit(2, "lines"))

cato_habitat_graph

```

CATO embed graph
```{r}
cato_embed <- cato %>%
  subset(characteristic=="embed") %>%
  mutate(x.axis=case_when(MonitoringLocationName=="Big Hunting Creek" ~ 1,
                          MonitoringLocationName=="Blue Blazes Creek" ~ 2,
                          MonitoringLocationName=="Owens Creek" ~ 3)) %>%
  mutate(value2=100-value)

cato_embed_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.1, xmax=3.6, ymin=45, ymax=100, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.1, xmax=3.6, ymin=0, ymax=45, fill="#f27c7e", alpha=0.5) +
  ##threshold line
  geom_hline(yintercept=45, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=cato_embed, aes(x=as.factor(x.axis), y=value2, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white")) +
  scale_x_discrete(labels=c("Big Hunting\nCreek", "Blue Blazes\nCreek", "Owens Creek"), guide=guide_axis(angle = 40)) +
  scale_y_continuous(labels=c(100, 75, 50, 25, 0)) +
  ##labels
  xlab("Stream") +
  ylab("Embeddedness (%)") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 100), xlim=c(0.1, 3.6), clip="off", expand=F) +
  ##score category labels
  annotate("text", x = 0.45, y = 22.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=5, fontface="italic") +
  annotate("text", x = 0.45, y = 72.5, angle = 90, vjust = 0,
           label = "Minimally impaired", color = "black", size=5, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=12),
        axis.title.y = element_text(size=20, vjust=3), 
        axis.title.x=element_text(size=20, vjust=-0.75),
        plot.margin=margin(t = 1, r = 1, b = 1, l = 1, unit = "cm"))

cato_embed_graph

```


PRWI habitat graph
```{r}
prwi <- sph %>%
  filter(!(MonitoringLocationName=="Middle Branch Chopawamsic Creek" | MonitoringLocationName=="North Branch Chopawamsic Creek")) %>%
  subset(Park=="PRWI" & (year==2011 | year==2021) & month>3) %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="embeddedness - percentage of rocks (gravel, cobble, boulders) covered by sediment (sand, silt)" ~ "embed",
                   CharacteristicName=="habitat quality - riffle" ~ "riffle",
                   CharacteristicName=="habitat quality - pool, glide, eddy" ~ "pool",
                   CharacteristicName=="habitat quality - water velocity and depth" ~ "velocity_depth",
                   CharacteristicName=="habitat quality - epifaunal substrate" ~ "epifaun",
                   CharacteristicName=="habitat quality - instream habitat" ~ "instream")) 

colnames(prwi)[5:6]=c("characteristic", "value")

prwi <- exceed(prwi)


prwi_habitat <- prwi %>%
  filter(!characteristic=="embed") %>%
  mutate(x.axis=case_when(characteristic=="epifaun" ~ 1,
                          characteristic=="instream" ~ 2,
                          characteristic=="pool" ~ 3,
                          characteristic=="riffle" ~ 4,
                          characteristic=="velocity_depth" ~ 5))

prwi_habitat_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.3, xmax=5.7, ymin=15, ymax=20, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=10, ymax=15, fill="#8ba7d6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=5, ymax=10, fill="#cf93b6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=0, ymax=5, fill="#f27c7e", alpha=0.5) +
  geom_hline(yintercept=5, linetype="dashed", color="gray55") +
  geom_hline(yintercept=10, linetype="dashed", color="gray55") +
  geom_hline(yintercept=15, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=prwi_habitat[!(prwi_habitat$MonitoringLocationName=="Boneyard Run" | prwi_habitat$MonitoringLocationName=="South Fork Quantico Creek" | prwi_habitat$MonitoringLocationName=="Sow Run"),], aes(x=as.factor(x.axis), y=value, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white")) +
  new_scale_fill() +
  new_scale_colour() +
  ##BONE, SFQC, SORU
  geom_bar(data=prwi_habitat[(prwi_habitat$MonitoringLocationName=="Boneyard Run" | prwi_habitat$MonitoringLocationName=="South Fork Quantico Creek" | prwi_habitat$MonitoringLocationName=="Sow Run"),], aes(x=as.factor(x.axis), y=value, fill=as.factor(year),
                                color=is_embed), width=0.35, size=0.8, 
           position=position_nudge(0.18), stat="identity") +
  scale_fill_manual(name="Year", values=c("white"), guide="none") +
  scale_color_manual(values=c("black", "#00000000"), guide="none") +
  ##facet grid
  facet_wrap2(.~MonitoringLocationName, axes="all", remove_labels="y",
              strip=strip_split("bottom")) +
  scale_x_discrete(labels=c("Epifaunal", "Instream", "Pool", "Riffle", "Velocity"),
                   guide=guide_axis(angle = 40)) +
  ##labels
  xlab("Stream") +
  ylab("Score") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 20), xlim=c(0.3, 5.7), clip="off", expand=F) +
  ###
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  ###
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 4) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 4) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 4) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 4) +
  ###
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 7) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 7) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 7) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 7) +
  ##repeating y axis label
  at_panel(annotate("text", x = -0.75, y = 10, angle = 90, vjust = 0,
           label = "Score", color = "black", size=7), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.75, y = 10, angle = 90, vjust = 0,
           label = "Score", color = "black", size=7), PANEL %in% 7) +
  ##theme
  theme_bw(base_size=15) +
  theme(strip.placement="outside",
        axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=12),
        axis.title.y = element_text(size=20, vjust=7),
        axis.title.x=element_text(size=20, vjust=-0.75), 
        strip.text = element_text(size=12),
        plot.margin=margin(t = 0.5, r = 1, b = 0.5, l = 1.5, unit = "cm"),
        panel.spacing=unit(2, "lines"))

prwi_habitat_graph

```

PRWI embed graph
```{r}
prwi_embed <- prwi %>%
  subset(characteristic=="embed") %>%
  mutate(x.axis=case_when(MonitoringLocationName=="Boneyard Run" ~ 1,
                          MonitoringLocationName=="Carters Run" ~ 2,
                          MonitoringLocationName=="Mary Byrd Branch" ~ 3,
                          MonitoringLocationName=="Mawavi Run" ~ 4,
                          MonitoringLocationName=="North Fork Quantico Creek" ~ 5,
                          MonitoringLocationName=="Orenda Run" ~ 6,
                          MonitoringLocationName=="South Fork Quantico Creek" ~ 7,
                          MonitoringLocationName=="Sow Run" ~ 8,
                          MonitoringLocationName=="Taylor Run" ~ 9)) %>%
  mutate(value2=100-value)

prwi_embed_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.1, xmax=9.6, ymin=45, ymax=100, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.1, xmax=9.6, ymin=0, ymax=45, fill="#f27c7e", alpha=0.5) +
  ##threshold line
  geom_hline(yintercept=45, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=prwi_embed[(prwi_embed$MonitoringLocationName=="Boneyard Run"),], aes(x=as.factor(x.axis), y=value2, fill=as.factor(year)), color="black", width=0.35, size=0.8, 
           position=position_nudge(0.18), stat="identity") +
  scale_fill_manual(name="Year", values=c("white", "gray60"), guide="none") +
  new_scale_fill() +
  new_scale_colour() +
  geom_bar(data=prwi_embed[!(prwi_embed$MonitoringLocationName=="Boneyard Run" | prwi_embed$MonitoringLocationName=="South Fork Quantico Creek" | prwi_embed$MonitoringLocationName=="Sow Run" | prwi_embed$MonitoringLocationName=="Taylor Run"),], aes(x=as.factor(x.axis), y=value2, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white")) +
  new_scale_fill() +
  new_scale_colour() +
  ##BONE, SFQC, SORU
  geom_bar(data=prwi_embed[(prwi_embed$MonitoringLocationName=="South Fork Quantico Creek" | prwi_embed$MonitoringLocationName=="Sow Run"),], aes(x=as.factor(x.axis), y=value2, fill=as.factor(year)), color="black", width=0.35, size=0.8, 
           position=position_nudge(0.18), stat="identity") +
  scale_fill_manual(name="Year", values=c("white", "gray60"), guide="none") +
  new_scale_fill() +
  new_scale_colour() +
  ##BONE, SFQC, SORU
  geom_bar(data=prwi_embed[(prwi_embed$MonitoringLocationName=="Taylor Run"),], aes(x=as.factor(x.axis), y=value2, fill=as.factor(year)), color="black", width=0.7, size=0.8, 
           position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white"), guide="none") +
  scale_x_discrete(labels=c("Boneyard Run", "Carters Run", "Mary Byrd\nBranch",
                            "Mawavi Run", "North Fork\nQuantico Creek",
                            "Orenda Run", "South Fork\nQuantico Creek",
                            "Sow Run", "Taylor Run"),
                   guide=guide_axis(angle=40)) +
  scale_y_continuous(labels=c(100, 75, 50, 25, 0)) +
  ##labels
  xlab("Stream") +
  ylab("Embeddedness (%)") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 100), xlim=c(0.1, 9.6), clip="off", expand=F) +
  ##score category labels
  annotate("text", x = 0.45, y = 22.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=5, fontface="italic") +
  annotate("text", x = 0.45, y = 72.5, angle = 90, vjust = 0,
           label = "Minimally impaired", color = "black", size=5, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=12),
        axis.title.y = element_text(size=20, vjust=3), 
        axis.title.x=element_text(size=20, vjust=-0.75),
        plot.margin=margin(t = 1, r = 1, b = 1, l = 1, unit = "cm"))

prwi_embed_graph

```


ANTI habitat graph
```{r}
anti <- sph %>%
  subset(Park=="ANTI" & (year==2013 | year==2022) & month>3) %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="embeddedness - percentage of rocks (gravel, cobble, boulders) covered by sediment (sand, silt)" ~ "embed",
                   CharacteristicName=="habitat quality - riffle" ~ "riffle",
                   CharacteristicName=="habitat quality - pool, glide, eddy" ~ "pool",
                   CharacteristicName=="habitat quality - water velocity and depth" ~ "velocity_depth",
                   CharacteristicName=="habitat quality - epifaunal substrate" ~ "epifaun",
                   CharacteristicName=="habitat quality - instream habitat" ~ "instream")) 

colnames(anti)[5:6]=c("characteristic", "value")

anti <- exceed(anti)


anti_habitat <- anti %>%
  filter(!characteristic=="embed") %>%
  mutate(x.axis=case_when(characteristic=="epifaun" ~ 1,
                          characteristic=="instream" ~ 2,
                          characteristic=="pool" ~ 3,
                          characteristic=="riffle" ~ 4,
                          characteristic=="velocity_depth" ~ 5))

anti_habitat_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0, xmax=5.7, ymin=15, ymax=20, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0, xmax=5.7, ymin=10, ymax=15, fill="#8ba7d6", alpha=0.5) +
  annotate("rect", xmin=0, xmax=5.7, ymin=5, ymax=10, fill="#cf93b6", alpha=0.5) +
  annotate("rect", xmin=0, xmax=5.7, ymin=0, ymax=5, fill="#f27c7e", alpha=0.5) +
  ##threshold lines
  geom_hline(yintercept=5, linetype="dashed", color="gray55") +
  geom_hline(yintercept=10, linetype="dashed", color="gray55") +
  geom_hline(yintercept=15, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=anti_habitat, aes(x=as.factor(x.axis), y=value, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white")) +
  scale_x_discrete(labels=c("Epifaunal", "Instream", "Pool", "Riffle", "Velocity"),
                   guide=guide_axis(angle = 40)) +
  ##labels
  xlab("Characteristic") +
  ylab("Score") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 20), xlim=c(0, 5.7), clip="off", expand=F) +
  ##habitat quality color scale
  annotate("text", x = 0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic") +
  annotate("text", x = 0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic") +
  annotate("text", x = 0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic") +
  annotate("text", x = 0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(strip.placement="outside",
        axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=14),
        axis.title.y = element_text(size=20),
        axis.title.x=element_text(size=20, vjust=-0.75), 
        strip.text = element_text(size=15),
        plot.margin=margin(t = 0.5, r = 1, b = 0.5, l = 1.5, unit = "cm"),
        panel.spacing=unit(2, "lines"))

anti_habitat_graph

```

ANTI embed graph
```{r}
anti_embed <- anti %>%
  subset(characteristic=="embed") %>%
  mutate(x.axis=case_when(MonitoringLocationName=="Sharpsburg Creek" ~ 1)) %>%
  mutate(value2=100-value)

anti_embed_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.4, xmax=1.6, ymin=45, ymax=100, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.4, xmax=1.6, ymin=0, ymax=45, fill="#f27c7e", alpha=0.5) +
  ##threshold line
  geom_hline(yintercept=45, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=anti_embed, aes(x=as.factor(x.axis), y=value2, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white")) +
  scale_x_discrete(labels=c("")) +
  scale_y_continuous(labels=c(100, 75, 50, 25, 0)) +
  ##labels
  xlab("Sharpsburg Creek") +
  ylab("Embeddedness (%)") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 100), xlim=c(0.4, 1.6), clip="off", expand=F) +
  ##score category labels
  annotate("text", x = 0.55, y = 22.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=5, fontface="italic") +
  annotate("text", x = 0.55, y = 72.5, angle = 90, vjust = 0,
           label = "Minimally impaired", color = "black", size=5, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=12),
        axis.title.y = element_text(size=20, vjust=3), 
        axis.title.x=element_text(size=15, vjust=4),
        axis.ticks.x = element_blank(),
        plot.margin=margin(t = 1, r = 1, b = 1, l = 1, unit = "cm"))

anti_embed_graph

```


GWMP habitat graph
```{r}
gwmp <- sph %>%
  subset(Park=="GWMP" & (year==2009 | year==2012 | year==2022) & month>4) %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="embeddedness - percentage of rocks (gravel, cobble, boulders) covered by sediment (sand, silt)" ~ "embed",
                   CharacteristicName=="habitat quality - riffle" ~ "riffle",
                   CharacteristicName=="habitat quality - pool, glide, eddy" ~ "pool",
                   CharacteristicName=="habitat quality - water velocity and depth" ~ "velocity_depth",
                   CharacteristicName=="habitat quality - epifaunal substrate" ~ "epifaun",
                   CharacteristicName=="habitat quality - instream habitat" ~ "instream")) %>%
  mutate(year2=case_when(year==2009~2012,
                         year!=2009~year)) %>%
  mutate(name2=case_when(MonitoringLocationName=="Minnehaha Creek"~"Minnehaha Creek*",
                         MonitoringLocationName!="Minnehaha Creek"~MonitoringLocationName))

colnames(gwmp)[5:6]=c("characteristic", "value")

gwmp <- exceed(gwmp)


gwmp_habitat <- gwmp %>%
  filter(!characteristic=="embed") %>%
  mutate(x.axis=case_when(characteristic=="epifaun" ~ 1,
                          characteristic=="instream" ~ 2,
                          characteristic=="pool" ~ 3,
                          characteristic=="riffle" ~ 4,
                          characteristic=="velocity_depth" ~ 5))

gwmp_habitat_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.3, xmax=5.7, ymin=15, ymax=20, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=10, ymax=15, fill="#8ba7d6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=5, ymax=10, fill="#cf93b6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=0, ymax=5, fill="#f27c7e", alpha=0.5) +
  ##threshold lines
  geom_hline(yintercept=5, linetype="dashed", color="gray55") +
  geom_hline(yintercept=10, linetype="dashed", color="gray55") +
  geom_hline(yintercept=15, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=gwmp_habitat, aes(x=as.factor(x.axis), y=value, fill=as.factor(year2)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white"), 
                    labels=c("2012, *09", "2022")) +
  ##facet grid
  facet_wrap2(.~name2, axes="all", remove_labels="y",
              strip=strip_split("bottom")) +
  scale_x_discrete(labels=c("Epifaunal", "Instream", "Pool", "Riffle", "Velocity"),
                   guide=guide_axis(angle = 40)) +
  ##labels
  xlab("Stream") +
  ylab("Score") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 20), xlim=c(0.3, 5.7), clip="off", expand=F) +
  ##habitat quality color scale
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 3) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 3) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 3) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 3) +
  ##theme
  theme_bw(base_size=15) +
  theme(strip.placement="outside",
        axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=10),
        axis.title.y = element_text(size=20, vjust=7),
        axis.title.x=element_text(size=20, vjust=-0.75), 
        strip.text = element_text(size=15),
        plot.margin=margin(t = 0.5, r = 1, b = 0.5, l = 1.5, unit = "cm"),
        panel.spacing=unit(2, "lines"))

gwmp_habitat_graph

```

GWMP embed graph
```{r}
gwmp_embed <- gwmp %>%
  subset(characteristic=="embed") %>%
  mutate(x.axis=case_when(MonitoringLocationName=="Mine Run" ~ 1,
                          MonitoringLocationName=="Minnehaha Creek" ~ 2,
                          MonitoringLocationName=="Pimmit Run" ~ 3,
                          MonitoringLocationName=="Turkey Run"~4)) %>%
  mutate(value2=100-value)

gwmp_embed_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.1, xmax=4.6, ymin=45, ymax=100, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.1, xmax=4.6, ymin=0, ymax=45, fill="#f27c7e", alpha=0.5) +
  ##threshold line
  geom_hline(yintercept=45, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=gwmp_embed, aes(x=as.factor(x.axis), y=value2, fill=as.factor(year2)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white"),
                    labels=c("2012, *09", "2022")) +
  scale_x_discrete(labels=c("Mine Run", "Minnehaha\nCreek*", "Pimmit Run", "Turkey Run"), guide=guide_axis(angle = 40)) +
  scale_y_continuous(labels=c(100, 75, 50, 25, 0)) +
  ##labels
  xlab("Stream") +
  ylab("Embeddedness (%)") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 100), xlim=c(0.1, 4.6), clip="off", expand=F) +
  ##score category labels
  annotate("text", x = 0.45, y = 22.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=5, fontface="italic") +
  annotate("text", x = 0.45, y = 72.5, angle = 90, vjust = 0,
           label = "Minimally impaired", color = "black", size=5, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=12),
        axis.title.y = element_text(size=20, vjust=3), 
        axis.title.x=element_text(size=20, vjust=-0.75),
        plot.margin=margin(t = 1, r = 1, b = 1, l = 1, unit = "cm"))

gwmp_embed_graph

```


HAFE habitat graph
```{r}
hafe <- sph %>%
  subset(Park=="HAFE" & (year==2013 | year==2022) & month>3) %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="embeddedness - percentage of rocks (gravel, cobble, boulders) covered by sediment (sand, silt)" ~ "embed",
                   CharacteristicName=="habitat quality - riffle" ~ "riffle",
                   CharacteristicName=="habitat quality - pool, glide, eddy" ~ "pool",
                   CharacteristicName=="habitat quality - water velocity and depth" ~ "velocity_depth",
                   CharacteristicName=="habitat quality - epifaunal substrate" ~ "epifaun",
                   CharacteristicName=="habitat quality - instream habitat" ~ "instream")) 

colnames(hafe)[5:6]=c("characteristic", "value")

hafe <- exceed(hafe)


hafe_habitat <- hafe %>%
  filter(!characteristic=="embed") %>%
  mutate(x.axis=case_when(characteristic=="epifaun" ~ 1,
                          characteristic=="instream" ~ 2,
                          characteristic=="pool" ~ 3,
                          characteristic=="riffle" ~ 4,
                          characteristic=="velocity_depth" ~ 5))

hafe_habitat_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0, xmax=5.7, ymin=15, ymax=20, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0, xmax=5.7, ymin=10, ymax=15, fill="#8ba7d6", alpha=0.5) +
  annotate("rect", xmin=0, xmax=5.7, ymin=5, ymax=10, fill="#cf93b6", alpha=0.5) +
  annotate("rect", xmin=0, xmax=5.7, ymin=0, ymax=5, fill="#f27c7e", alpha=0.5) +
  ##threshold lines
  geom_hline(yintercept=5, linetype="dashed", color="gray55") +
  geom_hline(yintercept=10, linetype="dashed", color="gray55") +
  geom_hline(yintercept=15, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=hafe_habitat, aes(x=as.factor(x.axis), y=value, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white")) +
  scale_x_discrete(labels=c("Epifaunal", "Instream", "Pool", "Riffle", "Velocity"),
                   guide=guide_axis(angle = 40)) +
  ##labels
  xlab("Characteristic") +
  ylab("Score") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 20), xlim=c(0, 5.7), clip="off", expand=F) +
  ##habitat quality color scale
  annotate("text", x = 0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic") +
  annotate("text", x = 0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic") +
  annotate("text", x = 0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic") +
  annotate("text", x = 0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(strip.placement="outside",
        axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=14),
        axis.title.y = element_text(size=20),
        axis.title.x=element_text(size=20, vjust=-0.75), 
        strip.text = element_text(size=15),
        plot.margin=margin(t = 0.5, r = 1, b = 0.5, l = 1.5, unit = "cm"),
        panel.spacing=unit(2, "lines"))

hafe_habitat_graph

```

HAFE embed graph
```{r}
hafe_embed <- hafe %>%
  subset(characteristic=="embed") %>%
  mutate(x.axis=case_when(MonitoringLocationName=="Sharpsburg Creek" ~ 1)) %>%
  mutate(value2=100-value)

hafe_embed_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.4, xmax=1.6, ymin=45, ymax=100, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.4, xmax=1.6, ymin=0, ymax=45, fill="#f27c7e", alpha=0.5) +
  ##threshold line
  geom_hline(yintercept=45, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=hafe_embed, aes(x=as.factor(x.axis), y=value2, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white")) +
  scale_x_discrete(labels=c("")) +
  scale_y_continuous(labels=c(100, 75, 50, 25, 0)) +
  ##labels
  xlab("Flowing Springs Run") +
  ylab("Embeddedness (%)") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 100), xlim=c(0.4, 1.6), clip="off", expand=F) +
  ##score category labels
  annotate("text", x = 0.55, y = 22.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=5, fontface="italic") +
  annotate("text", x = 0.55, y = 72.5, angle = 90, vjust = 0,
           label = "Minimally impaired", color = "black", size=5, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=12),
        axis.title.y = element_text(size=20, vjust=3), 
        axis.title.x=element_text(size=15, vjust=4),
        axis.ticks.x = element_blank(),
        plot.margin=margin(t = 1, r = 1, b = 1, l = 1, unit = "cm"))

hafe_embed_graph

```


MANA habitat graph
```{r}
mana <- sph %>%
  subset(Park=="MANA" & (year==2010 | year==2022) & month>4) %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="embeddedness - percentage of rocks (gravel, cobble, boulders) covered by sediment (sand, silt)" ~ "embed",
                   CharacteristicName=="habitat quality - riffle" ~ "riffle",
                   CharacteristicName=="habitat quality - pool, glide, eddy" ~ "pool",
                   CharacteristicName=="habitat quality - water velocity and depth" ~ "velocity_depth",
                   CharacteristicName=="habitat quality - epifaunal substrate" ~ "epifaun",
                   CharacteristicName=="habitat quality - instream habitat" ~ "instream")) 

colnames(mana)[5:6]=c("characteristic", "value")

mana <- exceed(mana)


mana_habitat <- mana %>%
  filter(!characteristic=="embed") %>%
  mutate(x.axis=case_when(characteristic=="epifaun" ~ 1,
                          characteristic=="instream" ~ 2,
                          characteristic=="pool" ~ 3,
                          characteristic=="riffle" ~ 4,
                          characteristic=="velocity_depth" ~ 5))

mana_habitat_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0, xmax=5.7, ymin=15, ymax=20, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0, xmax=5.7, ymin=10, ymax=15, fill="#8ba7d6", alpha=0.5) +
  annotate("rect", xmin=0, xmax=5.7, ymin=5, ymax=10, fill="#cf93b6", alpha=0.5) +
  annotate("rect", xmin=0, xmax=5.7, ymin=0, ymax=5, fill="#f27c7e", alpha=0.5) +
  ##threshold lines
  geom_hline(yintercept=5, linetype="dashed", color="gray55") +
  geom_hline(yintercept=10, linetype="dashed", color="gray55") +
  geom_hline(yintercept=15, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=mana_habitat, aes(x=as.factor(x.axis), y=value, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white")) +
  scale_x_discrete(labels=c("Epifaunal", "Instream", "Pool", "Riffle", "Velocity"),
                   guide=guide_axis(angle = 40)) +
  ##labels
  xlab("Characteristic") +
  ylab("Score") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 20), xlim=c(0, 5.7), clip="off", expand=F) +
  ##habitat quality color scale
  annotate("text", x = 0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic") +
  annotate("text", x = 0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic") +
  annotate("text", x = 0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic") +
  annotate("text", x = 0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(strip.placement="outside",
        axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=14),
        axis.title.y = element_text(size=20),
        axis.title.x=element_text(size=20, vjust=-0.75), 
        strip.text = element_text(size=15),
        plot.margin=margin(t = 0.5, r = 1, b = 0.5, l = 1.5, unit = "cm"),
        panel.spacing=unit(2, "lines"))

mana_habitat_graph

```

MANA embed graph
```{r}
mana_embed <- mana %>%
  subset(characteristic=="embed") %>%
  mutate(x.axis=case_when(MonitoringLocationName=="Youngs Branch" ~ 1)) %>%
  mutate(value2=100-value)

mana_embed_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.4, xmax=1.6, ymin=45, ymax=100, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.4, xmax=1.6, ymin=0, ymax=45, fill="#f27c7e", alpha=0.5) +
  ##threshold line
  geom_hline(yintercept=45, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=mana_embed, aes(x=as.factor(x.axis), y=value2, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white")) +
  scale_x_discrete(labels=c("")) +
  scale_y_continuous(labels=c(100, 75, 50, 25, 0)) +
  ##labels
  xlab("Young's Branch") +
  ylab("Embeddedness (%)") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 100), xlim=c(0.4, 1.6), clip="off", expand=F) +
  ##score category labels
  annotate("text", x = 0.55, y = 22.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=5, fontface="italic") +
  annotate("text", x = 0.55, y = 72.5, angle = 90, vjust = 0,
           label = "Minimally impaired", color = "black", size=5, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=12),
        axis.title.y = element_text(size=20, vjust=3), 
        axis.title.x=element_text(size=15, vjust=4),
        axis.ticks.x = element_blank(),
        plot.margin=margin(t = 1, r = 1, b = 1, l = 1, unit = "cm"))

mana_embed_graph

```


MONO habitat graph
```{r}
mono <- sph %>%
  subset(Park=="MONO" & (year==2010 | year==2022) & month>4) %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="embeddedness - percentage of rocks (gravel, cobble, boulders) covered by sediment (sand, silt)" ~ "embed",
                   CharacteristicName=="habitat quality - riffle" ~ "riffle",
                   CharacteristicName=="habitat quality - pool, glide, eddy" ~ "pool",
                   CharacteristicName=="habitat quality - water velocity and depth" ~ "velocity_depth",
                   CharacteristicName=="habitat quality - epifaunal substrate" ~ "epifaun",
                   CharacteristicName=="habitat quality - instream habitat" ~ "instream")) 

colnames(mono)[5:6]=c("characteristic", "value")

mono <- exceed(mono)


mono_habitat <- mono %>%
  filter(!characteristic=="embed") %>%
  mutate(x.axis=case_when(characteristic=="epifaun" ~ 1,
                          characteristic=="instream" ~ 2,
                          characteristic=="pool" ~ 3,
                          characteristic=="riffle" ~ 4,
                          characteristic=="velocity_depth" ~ 5))

mono_habitat_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.3, xmax=5.7, ymin=15, ymax=20, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=10, ymax=15, fill="#8ba7d6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=5, ymax=10, fill="#cf93b6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=0, ymax=5, fill="#f27c7e", alpha=0.5) +
  ##threshold lines
  geom_hline(yintercept=5, linetype="dashed", color="gray55") +
  geom_hline(yintercept=10, linetype="dashed", color="gray55") +
  geom_hline(yintercept=15, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=mono_habitat, aes(x=as.factor(x.axis), y=value, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white"), 
                    labels=c("2010", "2022")) +
  ##facet grid
  facet_wrap2(.~MonitoringLocationName, axes="all", remove_labels="y",
              strip=strip_split("bottom")) +
  scale_x_discrete(labels=c("Epifaunal", "Instream", "Pool", "Riffle", "Velocity"),
                   guide=guide_axis(angle = 40)) +
  ##labels
  xlab("Stream") +
  ylab("Score") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 20), xlim=c(0.3, 5.7), clip="off", expand=F) +
  ##habitat quality color scale
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 3) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 3) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 3) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 3) +
  ##theme
  theme_bw(base_size=15) +
  theme(strip.placement="outside",
        axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=10),
        axis.title.y = element_text(size=20, vjust=7),
        axis.title.x=element_text(size=20, vjust=-0.75), 
        strip.text = element_text(size=15),
        plot.margin=margin(t = 0.5, r = 1, b = 0.5, l = 1.5, unit = "cm"),
        panel.spacing=unit(2, "lines"))

mono_habitat_graph

```

MONO embed graph
```{r}
mono_embed <- mono %>%
  subset(characteristic=="embed") %>%
  mutate(x.axis=case_when(MonitoringLocationName=="Bush Creek" ~ 1,
                          MonitoringLocationName=="Gambrill Mill Creek" ~ 2)) %>%
  mutate(value2=100-value)

mono_embed_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.3, xmax=2.6, ymin=45, ymax=100, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=2.6, ymin=0, ymax=45, fill="#f27c7e", alpha=0.5) +
  ##threshold line
  geom_hline(yintercept=45, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=mono_embed, aes(x=as.factor(x.axis), y=value2, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white"),
                    labels=c("2010", "2022")) +
  scale_x_discrete(labels=c("Bush Creek", "Gambrill\nMill Creek")) +
  scale_y_continuous(labels=c(100, 75, 50, 25, 0)) +
  ##labels
  xlab("Stream") +
  ylab("Embeddedness (%)") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 100), xlim=c(0.3, 2.6), clip="off", expand=F) +
  ##score category labels
  annotate("text", x = 0.5, y = 22.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=5, fontface="italic") +
  annotate("text", x = 0.5, y = 72.5, angle = 90, vjust = 0,
           label = "Minimally impaired", color = "black", size=5, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=14),
        axis.title.y = element_text(size=20, vjust=3), 
        axis.title.x=element_text(size=20, vjust=-0.75),
        plot.margin=margin(t = 1, r = 1, b = 1, l = 1, unit = "cm"))

mono_embed_graph

```


NACE habitat graph
```{r}
nace <- sph %>%
  subset(Park=="NACE" & (year==2013 | year==2022) & month>4) %>%
  filter(!MonitoringLocationName=="Accokeek Creek tributary") %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="embeddedness - percentage of rocks (gravel, cobble, boulders) covered by sediment (sand, silt)" ~ "embed",
                   CharacteristicName=="habitat quality - riffle" ~ "riffle",
                   CharacteristicName=="habitat quality - pool, glide, eddy" ~ "pool",
                   CharacteristicName=="habitat quality - water velocity and depth" ~ "velocity_depth",
                   CharacteristicName=="habitat quality - epifaunal substrate" ~ "epifaun",
                   CharacteristicName=="habitat quality - instream habitat" ~ "instream"))

colnames(nace)[5:6]=c("characteristic", "value")

nace <- exceed(nace)


nace_habitat <- nace %>%
  filter(!characteristic=="embed") %>%
  mutate(x.axis=case_when(characteristic=="epifaun" ~ 1,
                          characteristic=="instream" ~ 2,
                          characteristic=="pool" ~ 3,
                          characteristic=="riffle" ~ 4,
                          characteristic=="velocity_depth" ~ 5))

nace_habitat_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.3, xmax=5.7, ymin=15, ymax=20, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=10, ymax=15, fill="#8ba7d6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=5, ymax=10, fill="#cf93b6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=0, ymax=5, fill="#f27c7e", alpha=0.5) +
  ##threshold lines
  geom_hline(yintercept=5, linetype="dashed", color="gray55") +
  geom_hline(yintercept=10, linetype="dashed", color="gray55") +
  geom_hline(yintercept=15, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=nace_habitat, aes(x=as.factor(x.axis), y=value, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white"), 
                    labels=c("2013", "2022")) +
  ##facet grid
  facet_wrap2(.~MonitoringLocationName, axes="all", remove_labels="y",
              strip=strip_split("bottom")) +
  scale_x_discrete(labels=c("Epifaunal", "Instream", "Pool", "Riffle", "Velocity"),
                   guide=guide_axis(angle = 40)) +
  ##labels
  xlab("Stream") +
  ylab("Score") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 20), xlim=c(0.3, 5.7), clip="off", expand=F) +
  ##habitat quality color scale
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  ##theme
  theme_bw(base_size=15) +
  theme(strip.placement="outside",
        axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=10),
        axis.title.y = element_text(size=20, vjust=7),
        axis.title.x=element_text(size=20, vjust=-0.75), 
        strip.text = element_text(size=15),
        plot.margin=margin(t = 0.5, r = 1, b = 0.5, l = 1.5, unit = "cm"),
        panel.spacing=unit(2, "lines"))

nace_habitat_graph

```

NACE embed graph
```{r}
nace_embed <- nace %>%
  subset(characteristic=="embed") %>%
  mutate(x.axis=case_when(MonitoringLocationName=="Henson Creek" ~ 1,
                          MonitoringLocationName=="Oxon Run" ~ 2,
                          MonitoringLocationName=="Still Creek" ~ 3)) %>%
  mutate(value2=100-value)

nace_embed_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.1, xmax=3.6, ymin=45, ymax=100, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.1, xmax=3.6, ymin=0, ymax=45, fill="#f27c7e", alpha=0.5) +
  ##threshold line
  geom_hline(yintercept=45, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=nace_embed, aes(x=as.factor(x.axis), y=value2, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white"),
                    labels=c("2013", "2022")) +
  scale_x_discrete(labels=c("Henson\nCreek", "Oxon\nRun", "Still\nCreek")) +
  scale_y_continuous(labels=c(100, 75, 50, 25, 0)) +
  ##labels
  xlab("Stream") +
  ylab("Embeddedness (%)") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 100), xlim=c(0.1, 3.6), clip="off", expand=F) +
  ##score category labels
  annotate("text", x = 0.45, y = 22.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=5, fontface="italic") +
  annotate("text", x = 0.45, y = 72.5, angle = 90, vjust = 0,
           label = "Minimally impaired", color = "black", size=5, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=12),
        axis.title.y = element_text(size=20, vjust=3), 
        axis.title.x=element_text(size=20, vjust=-0.75),
        plot.margin=margin(t = 1, r = 1, b = 1, l = 1, unit = "cm"))

nace_embed_graph

```


ROCR habitat graph
```{r}
rocr <- sph %>%
  subset(Park=="ROCR" & (year==2008 | year==2009 | year==2019 | year==2022) & month>4) %>%
  filter(!MonitoringLocationName=="Soapstone Valley Stream") %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="embeddedness - percentage of rocks (gravel, cobble, boulders) covered by sediment (sand, silt)" ~ "embed",
                   CharacteristicName=="habitat quality - riffle" ~ "riffle",
                   CharacteristicName=="habitat quality - pool, glide, eddy" ~ "pool",
                   CharacteristicName=="habitat quality - water velocity and depth" ~ "velocity_depth",
                   CharacteristicName=="habitat quality - epifaunal substrate" ~ "epifaun",
                   CharacteristicName=="habitat quality - instream habitat" ~ "instream")) %>%
  mutate(year2=case_when(year==2008~"year1",
                         year==2009~"year1",
                         year==2019~"year2",
                         year==2022~"year2")) %>%
  mutate(name2=case_when(Site=="BAKE"~"Battery Kemble Run*‡",
                         Site=="BRBR"~"Broad Branch",
                         Site=="DUOA"~"Dumbarton Oaks*",
                         Site=="FEBR"~"Fenwick Branch",
                         Site=="KLVA"~"Klingle Valley*",
                         Site=="LUBR"~"Luzon Branch",
                         Site=="NOST"~"Normanstone Branch*",
                         Site=="PHBR"~"Pinehurst Branch",
                         Site=="PYBR"~"Piney Branch*",
                         Site=="R630"~"Reservation 630",
                         Site=="ROC3"~"Rock Creek Downstream\nof Dumbarton Oaks‡"))

colnames(rocr)[5:6]=c("characteristic", "value")

rocr <- exceed(rocr)


rocr_habitat <- rocr %>%
  filter(!characteristic=="embed") %>%
  mutate(x.axis=case_when(characteristic=="epifaun" ~ 1,
                          characteristic=="instream" ~ 2,
                          characteristic=="pool" ~ 3,
                          characteristic=="riffle" ~ 4,
                          characteristic=="velocity_depth" ~ 5))

rocr_habitat_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.3, xmax=5.7, ymin=15, ymax=20, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=10, ymax=15, fill="#8ba7d6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=5, ymax=10, fill="#cf93b6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=0, ymax=5, fill="#f27c7e", alpha=0.5) +
  geom_hline(yintercept=5, linetype="dashed", color="gray55") +
  geom_hline(yintercept=10, linetype="dashed", color="gray55") +
  geom_hline(yintercept=15, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=rocr_habitat[!rocr_habitat$Site=="ROC3",], aes(x=as.factor(x.axis), y=value, fill=year2), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white"),
                    labels=c("2008, *09", "2019, ‡22")) +
  new_scale_fill() +
  new_scale_colour() +
  ##ROC3
  geom_bar(data=rocr_habitat[(rocr_habitat$Site=="ROC3"),], aes(x=as.factor(x.axis), y=value, fill=as.factor(year),
                                color=is_embed), width=0.35, size=0.8, 
           position=position_nudge(0.18), stat="identity") +
  scale_fill_manual(name="Year", values=c("white"), guide="none") +
  scale_color_manual(values=c("black", "#00000000"), guide="none") +
  ##facet grid
  facet_wrap2(.~name2, axes="all", remove_labels="y",
              strip=strip_split("bottom"), ncol=3) +
  scale_x_discrete(labels=c("Epifaunal", "Instream", "Pool", "Riffle", "Velocity"),
                   guide=guide_axis(angle = 40)) +
  ##labels
  xlab("Stream") +
  ylab("") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 20), xlim=c(0.3, 5.7), clip="off", expand=F) +
  ###
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  ###
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 4) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 4) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 4) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 4) +
  ###
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 7) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 7) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 7) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 7) +
  ###
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 10) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 10) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 10) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 10) +
  #repeating y axis label
  at_panel(annotate("text", x = -0.75, y = 10, angle = 90, vjust = 0,
           label = "Score", color = "black", size=7), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.75, y = 10, angle = 90, vjust = 0,
           label = "Score", color = "black", size=7), PANEL %in% 4) +
  at_panel(annotate("text", x = -0.75, y = 10, angle = 90, vjust = 0,
           label = "Score", color = "black", size=7), PANEL %in% 7) +
  at_panel(annotate("text", x = -0.75, y = 10, angle = 90, vjust = 0,
           label = "Score", color = "black", size=7), PANEL %in% 10) +
  #theme
  theme_bw(base_size=15) +
  theme(strip.placement="outside",
        axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=12),
        axis.title.y = element_text(size=20, vjust=7),
        axis.title.x=element_text(size=20, vjust=-0.75), 
        strip.text = element_text(size=12),
        plot.margin=margin(t = 0.5, r = 1, b = 0.5, l = 1.5, unit = "cm"),
        panel.spacing=unit(2, "lines"))

rocr_habitat_graph

##plot dimensions: 1500x2200

```

ROCR embed graph
```{r}
rocr_embed <- rocr %>%
  subset(characteristic=="embed") %>%
  mutate(x.axis=case_when(Site=="BAKE"~1,
                          Site=="BRBR"~2,
                          Site=="DUOA"~3,
                          Site=="FEBR"~4,
                          Site=="KLVA"~5,
                          Site=="LUBR"~6,
                          Site=="NOST"~7,
                          Site=="PHBR"~8,
                          Site=="PYBR"~9,
                          Site=="R630"~10,
                          Site=="ROC3"~11,)) %>%
  mutate(value2=100-value)

rocr_names <- c("Battery Kemble\nRun*‡", "Broad Branch", 
                "Dumbarton Oaks*", "Fenwick Branch", "Klingle Valley*",
                "Luzon Branch", "Normanstone Branch*", 
                "Pinehurst Branch", "Piney Branch*", "Reservation 630",
                "Rock Creek\nDownstream of\nDumbarton Oaks‡")

rocr_embed_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.1, xmax=11.6, ymin=45, ymax=100, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.1, xmax=11.6, ymin=0, ymax=45, fill="#f27c7e", alpha=0.5) +
  ##threshold line
  geom_hline(yintercept=45, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=rocr_embed[!rocr_embed$Site=="ROC3",], aes(x=as.factor(x.axis), y=value2, fill=year2), color="black", width=0.7, size=0.8, 
           position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white"),
                    labels=c("2008, *09", "2019, ‡22")) +
  new_scale_fill() +
  new_scale_colour() +
  ##ROC3
  geom_bar(data=rocr_embed[rocr_embed$Site=="ROC3",], aes(x=as.factor(x.axis), y=value2, fill=year2), 
           color="black", width=0.35, size=0.8, position=position_nudge(0.18), stat="identity") +
  scale_fill_manual(name="Year", values=c("white", "gray60"),
                    guide="none") +
  scale_x_discrete(labels=c(rocr_names),
                   guide=guide_axis(angle=40)) +
  scale_y_continuous(labels=c(100, 75, 50, 25, 0)) +
  ##labels
  xlab("Stream") +
  ylab("Embeddedness (%)") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 100), xlim=c(0.1, 11.6), clip="off", expand=F) +
  ##score category labels
  annotate("text", x = 0.45, y = 22.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=5, fontface="italic") +
  annotate("text", x = 0.45, y = 72.5, angle = 90, vjust = 0,
           label = "Minimally impaired", color = "black", size=5, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=12),
        axis.title.y = element_text(size=20, vjust=3), 
        axis.title.x=element_text(size=20, vjust=-0.75),
        plot.margin=margin(t = 1, r = 1, b = 1, l = 1, unit = "cm"))

rocr_embed_graph

##plot dimensions: 1200x700

```


WOTR habitat graph
```{r}
wotr <- sph %>%
  subset(Park=="WOTR" & (year==2012 | year==2022) & month>4) %>%
  mutate(CharacteristicName=case_when(CharacteristicName=="embeddedness - percentage of rocks (gravel, cobble, boulders) covered by sediment (sand, silt)" ~ "embed",
                   CharacteristicName=="habitat quality - riffle" ~ "riffle",
                   CharacteristicName=="habitat quality - pool, glide, eddy" ~ "pool",
                   CharacteristicName=="habitat quality - water velocity and depth" ~ "velocity_depth",
                   CharacteristicName=="habitat quality - epifaunal substrate" ~ "epifaun",
                   CharacteristicName=="habitat quality - instream habitat" ~ "instream")) 

colnames(wotr)[5:6]=c("characteristic", "value")

wotr <- exceed(wotr)


wotr_habitat <- wotr %>%
  filter(!characteristic=="embed") %>%
  mutate(x.axis=case_when(characteristic=="epifaun" ~ 1,
                          characteristic=="instream" ~ 2,
                          characteristic=="pool" ~ 3,
                          characteristic=="riffle" ~ 4,
                          characteristic=="velocity_depth" ~ 5))

wotr_habitat_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.3, xmax=5.7, ymin=15, ymax=20, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=10, ymax=15, fill="#8ba7d6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=5, ymax=10, fill="#cf93b6", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=5.7, ymin=0, ymax=5, fill="#f27c7e", alpha=0.5) +
  ##threshold lines
  geom_hline(yintercept=5, linetype="dashed", color="gray55") +
  geom_hline(yintercept=10, linetype="dashed", color="gray55") +
  geom_hline(yintercept=15, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=wotr_habitat, aes(x=as.factor(x.axis), y=value, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white"), 
                    labels=c("2012", "2022")) +
  ##facet grid
  facet_wrap2(.~MonitoringLocationName, axes="all", remove_labels="y",
              strip=strip_split("bottom")) +
  scale_x_discrete(labels=c("Epifaunal", "Instream", "Pool", "Riffle", "Velocity"),
                   guide=guide_axis(angle = 40)) +
  ##labels
  xlab("Stream") +
  ylab("Score") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 20), xlim=c(0.3, 5.7), clip="off", expand=F) +
  ##habitat quality color scale
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 1) +
  at_panel(annotate("text", x = -0.3, y = 2.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=4, fontface="italic"), PANEL %in% 3) +
  at_panel(annotate("text", x = -0.3, y = 7.5, angle = 90, vjust = 0,
           label = "Marginal", color = "black", size=4, fontface="italic"), PANEL %in% 3) +
  at_panel(annotate("text", x = -0.3, y = 12.5, angle = 90, vjust = 0,
           label = "Suboptimal", color = "black", size=4, fontface="italic"), PANEL %in% 3) +
  at_panel(annotate("text", x = -0.3, y = 17.5, angle = 90, vjust = 0,
           label = "Optimal", color = "black", size=4, fontface="italic"), PANEL %in% 3) +
  ##theme
  theme_bw(base_size=15) +
  theme(strip.placement="outside",
        axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=10),
        axis.title.y = element_text(size=20, vjust=7),
        axis.title.x=element_text(size=20, vjust=-0.75), 
        strip.text = element_text(size=15),
        plot.margin=margin(t = 0.5, r = 1, b = 0.5, l = 1.5, unit = "cm"),
        panel.spacing=unit(2, "lines"))

wotr_habitat_graph

```

WOTR embed graph
```{r}
wotr_embed <- wotr %>%
  subset(characteristic=="embed") %>%
  mutate(x.axis=case_when(MonitoringLocationName=="Courthouse Creek" ~ 1,
                          MonitoringLocationName=="Wolf Trap Creek" ~ 2)) %>%
  mutate(value2=100-value)

wotr_embed_graph <- ggplot() +
  ##background regions
  annotate("rect", xmin=0.3, xmax=2.6, ymin=45, ymax=100, fill="#7dc7ff", alpha=0.5) +
  annotate("rect", xmin=0.3, xmax=2.6, ymin=0, ymax=45, fill="#f27c7e", alpha=0.5) +
  ##threshold line
  geom_hline(yintercept=45, linetype="dashed", color="gray55") +
  ##bar graph
  geom_bar(data=wotr_embed, aes(x=as.factor(x.axis), y=value2, fill=as.factor(year)), 
           color="black", width=0.7, size=0.8, position="dodge", stat="identity") +
  scale_fill_manual(name="Year", values=c("gray60", "white"),
                    labels=c("2012", "2022")) +
  scale_x_discrete(labels=c("Courthouse\nCreek", "Wolf Trap\nCreek")) +
  scale_y_continuous(labels=c(100, 75, 50, 25, 0)) +
  ##labels
  xlab("Stream") +
  ylab("Embeddedness (%)") +
  ##setting graph boundaries
  coord_cartesian(ylim=c(0, 100), xlim=c(0.3, 2.6), clip="off", expand=F) +
  ##score category labels
  annotate("text", x = 0.5, y = 22.5, angle = 90, vjust = 0,
           label = "Poor", color = "black", size=5, fontface="italic") +
  annotate("text", x = 0.5, y = 72.5, angle = 90, vjust = 0,
           label = "Minimally impaired", color = "black", size=5, fontface="italic") +
  ##theme
  theme_bw(base_size=15) +
  theme(axis.text.y=element_text(size=12),
        axis.text.x=element_text(size=14),
        axis.title.y = element_text(size=20, vjust=3), 
        axis.title.x=element_text(size=20, vjust=-0.75),
        plot.margin=margin(t = 1, r = 1, b = 1, l = 1, unit = "cm"))

wotr_embed_graph

```

